### 2014-04-23 Response_to_R0_Reviews.tex

    We have also emphasized that the imaging was performed endorectally by
    modifying the following statement in the same section:

    \textbf{3D volumetric imaging data was acquired endorectally\ldots}

    \item \textit{Why were the tracking beams focused (@ 60 mm) twice as deep
            as the pushing beams (@ 30 mm and above)?  It would seem that the
            radiation force would not propagate this far below the pushing
            focal position. (pg 6 lines 163 and 154, respectively).}

    The tracking beam transmit was focused at 60 mm to insonify a large lateral
    field of view and observe the off-axis shear wave propagation with the
    remaining 12 parallel receive beams that were not utilized in this work
    (lines 160-161). For each track beam, dynamic receive and receive aperture
    growth with a F/0.5 configuration were used to minimize the effect of the
    deep transmit focus.  Since only the ARFI imaging vectors were presented in
    this work--not the shear wave data--we have not ammended the manuscript
    text to avoid confusing the reader with details not relevant to the data
    presented in this manuscript.

### 2014-04-23 Response_to_R0_Reviews.tex

    \item \textit{Why were the tracking beams focused (@ 60 mm) twice as deep
            as the pushing beams (@ 30 mm and above)?  It would seem that the
            radiation force would not propagate this far below the pushing
            focal position. (pg 6 lines 163 and 154, respectively).}

    The tracking beam transmit was focused at 60 mm to insonify a large lateral
    field of view and observe the off-axis shear wave propagation with the
    remaining 12 parallel receive beams that were not utilized in this work
    (lines 160-161). For each track beam, dynamic receive and receive aperture
    growth with a F/0.5 configuration were used to minimize the effect of the
    deep transmit focus.  Since only the ARFI imaging vectors were presented in
    this work--not the shear wave data--we have not ammended the manuscript
    text to avoid confusing the reader with details not relevant to the data
    presented in this manuscript.

    \item \textit{For the displacement normalization factor derived in phantom
            materials (pg 7 lines 176-177), what were the acoustic and
            mechanical properties of the phantom, and were these well matched
            to the expected properties of prostate tissue?  How much are these
            properties expected to vary from individual to individual, with or
            without prostate cancer?  What would the impact of using of an
            incorrect normalization factor be on the overall ARFI results?  The
            authors should consider adding a discussion of the potential impact
            of the assumed normalization factor to the limitations sections.}

    This is a great comment, and one that we have considered internally during
    the development of our methodology for this study.  The normalization
    profile for ARFI images is similar in concept to time gain compensation
    (TGC) for B-mode images. It is used to apply gain throughout the image to
    provide a more uniform appearance of the image through depth, which is
    necessary to account for tissue attenuation and focal gain. The
    normalization does not change the raw image data since it is applying
    digital gain. Additionally, when a reader views the images, gain can be
    added or removed as desired to further improve the image quality.
    Therefore, on a patient-by-patient basis, the normalization profile can be
    adjusted to account for differences in each individual to reduce the impact
    of having an incorrect normalization profile.

    Specifically, for this work, two calibrated CIRS (Norfolk, VA) elasticity
    phantoms were used to determine the normalization factor; the background
    stiffness of both materials was nominally 10 kPa Young's modulus, and the
    acoustic attenuation of the two phantoms were 0.49 and 0.72 dB/cm/MHz,
    respectively. The displacement-through-time profiles from each phantom were
    averaged together to approximate a 10 kPa Young's modulus with a 0.6
    dB/cm/MHz attenuation. The phantom stiffness is slightly lower than the
    12.3 kPa Young's modulus reported as healthy peripheral zone tissue [1].
    The attenuation coefficient for prostatic tissue has been reported as
    0.54-1.04 dB/cm/MHz [2], with additional support that the attenuation is at
    the lower end of that range [3]. Thus, the normalization profile closely
    approximates the properties of healthy peripheral zone prostatic tissue,
    but the transition and central zones as well as pathology such as cancer,
    BPH, or atrophy can all potentially have different mechanical and
    acoustical properties.

    [1] Zhai, Liang, et al. ``Correlation between SWEI and ARFI image findings
    in ex vivo human prostates.'' Ultrasonics Symposium (IUS), 2009 IEEE
    International. IEEE, 2009.

    [2] K.J Parker, S.R Huang, R.M Lerner et al. Elastic and ultrasonic
    properties of the prostate IEEE Ultrason Sympos Proc, 2 (1993), pp.
    1035–1038

    [3] A.E Worthington, J Trachtenberg, M.D Sherar, Ultrasound properties of
    human prostate tissue during heating, Ultrasound in Medicine \& Biology,
    Volume 28, Issue 10, October 2002, Pages 1311-1318.

### 2014-04-24 Response_to_R0_Reviews.tex

    \item \textit{How many readers performed the B-Mode and ARFI segmentation
            per image? per entire study data set? Were the readers trained, and
            if so, how?  Did different readers segment the B-Mode and ARFI data
            sets?  Did the same radiologist who segmented the MRI images also
            segment the B-Mode and ARFI data?}

    All of the B-mode and ARFI images were segemented by two individuals (ZAM,
    TJG), and reviewed by a single, experienced ARFI imaging research (KRN).
    There was no formal training in reading the ARFI images since this work is
    our first effort to analyze our ability to evaluate our accuracy in
    identifying structures in ARFI prostate images.  The same individuals
    segmented both the B-mode images (for the capsules) and ARFI images (for
    the central glands).  All of the MR images were segmented by an experienced
    radiology fellow (CK) and reviewed by an experienced prostate radiologist
    (RG).  We have added the following text to the manuscript to delineate the
    readers / image segmenters for each part of the study (Section III(E.1)):

    Axial MR T2WI images were manually segmented by a \textbf{single
        radiologist (CK)} using the smooth polygon tool in ITK-SNAP\ldots

    \textbf{All MR image segmentations were ultimately reviewed by an
        experienced prostate radiologist (RTG).}

    And Section III(E.2):

    Sagittal B-mode and ARFI ultrasound image stacks were segmented in 3D
    Slicer \textbf{by two researchers (TJG \& ZAM)}\ldots

    \textbf{All B-mode and ARFI image segmentations were reviewed by an
        experienced ARFI imaging researcher (KRN).}

### 2014-04-24 image_proc_methods.tex
responded about number of segmenters for each imaging modality

\subsection{Image Zonal Anatomy Segmentation and 3D Model Rendering}
\subsubsection{MR Image Segmentation and Modeling}
Axial MR T2WI images were manually segmented by an experienced radiologist
using the smooth polygon tool in ITK-SNAP
(http://www.itksnap.org)~\cite{Yushkevich2006}, using unique labels for
the PZ, CG and AFS. The gland was segmented from base-to-apex.  The base was
identified below the bladder, and subsequent images were segmented until the
last slice with visible prostatic tissue was identified caudally. The CG,
urethra, PZ and AFS were segmented independently according to their
well-established anatomical characteristics on
T2WI.~\cite{Barentsz2012,Jung2012,Poon1985,Hricak2007,Bonekamp2011} The PZ was
identified by its homogeneous high signal intensity on T2WI, which is usually
similar to that of the nearby peri-prostatic fat. The CG was visualized and
delineated based on its heterogeneous, lower signal intensity and its location
(Figure~\ref{fig:mr_anatomy}). The urethra was included in the CG segmentation.
When visible, the AFS was identified by its low T2 signal intensity and its
location anterior to the CG.

@@

\subsubsection{Ultrasound Image Segmentation and Modeling}
Sagittal B-mode and ARFI ultrasound image stacks were segmented in 3D Slicer
using the \verb+draweffect+ tool to model and measure the prostate capsule and
CG volume and tri-axial dimensions (Figure~\ref{fig:arfi_segs}).  The sagittal
imaging plane was chosen for segmentation because it has a greater number of
easily identifiable anatomical structures:  seminal vesicles in the left and
right posterior base, urethra in the mid apex, surrounding fibromuscular tissue
in the anterior, and rectum in the posterior. Prostate capsule was segmented in
B-mode as this modality offers both high contrast between prostatic tissue and
surrounding peri-prostatic fat, and better SNR in the anterior capsule region
than ARFI images. ARFI images were used for CG segmentation.  Prior to
segmentation, both the B-mode and ARFI image stacks were down-sampled along the
sagittal axis to a slice thickness of 3 mm to reduce the number of
manually-segmented frames (18 vs. 360 slices / image stack) and match the MRI
slice thickness.

While segmentations were performed along the sagittal plane, label map
intersections in the axial and coronal views were used during active creation
of the sagittal segmentation to further improve segmentation accuracy.
Parameters used for 3D model rendering were identical to those used for MR
modeling (Table~\ref{tab:3dslicer}).  The modeled capsule helped guide the CG
segmentation by enabling capsule model intersections in the three orthogonal
planes during CG segmentation (Figure~\ref{fig:arfi_segs}). The capsule
provided an outer boundary for the CG segmentation. The capsule and CG models
dimensions were then measured using the same procedure as the MR images.

>>>>

\subsection{Image Zonal Anatomy Segmentation and 3D Model Rendering}
\subsubsection{MR Image Segmentation and Modeling}
Axial MR T2WI images were manually segmented by a \textbf{single radiologist
    (CK)} using the smooth polygon tool in ITK-SNAP
(http://www.itksnap.org)~\cite{Yushkevich2006}, using unique labels for the PZ,
CG and AFS. The gland was segmented from base-to-apex.  The base was identified
below the bladder, and subsequent images were segmented until the last slice
with visible prostatic tissue was identified caudally. The CG, urethra, PZ and
AFS were segmented independently according to their well-established anatomical
characteristics on
T2WI.~\cite{Barentsz2012,Jung2012,Poon1985,Hricak2007,Bonekamp2011} The PZ was
identified by its homogeneous high signal intensity on T2WI, which is usually
similar to that of the nearby peri-prostatic fat. The CG was visualized and
delineated based on its heterogeneous, lower signal intensity and its location
(Figure~\ref{fig:mr_anatomy}). The urethra was included in the CG segmentation.
When visible, the AFS was identified by its low T2 signal intensity and its
location anterior to the CG.  \textbf{All MR image segmentations were
    ultimately reviewed by an experienced prostate radiologist (RTG).}

@@

\subsubsection{Ultrasound Image Segmentation and Modeling}
\Sagittal B-mode and ARFI ultrasound image stacks were segmented in 3D Slicer
\textbf{by two researchers (TJG \& ZAM)} using the \verb+draweffect+ tool to model and measure the prostate capsule and
CG volume and tri-axial dimensions (Figure~\ref{fig:arfi_segs}).  The sagittal
imaging plane was chosen for segmentation because it has a greater number of
easily identifiable anatomical structures:  seminal vesicles in the left and
right posterior base, urethra in the mid apex, surrounding fibromuscular tissue
in the anterior, and rectum in the posterior. Prostate capsule was segmented in
B-mode as this modality offers both high contrast between prostatic tissue and
surrounding peri-prostatic fat, and better SNR in the anterior capsule region
than ARFI images. ARFI images were used for CG segmentation.  Prior to
segmentation, both the B-mode and ARFI image stacks were down-sampled along the
sagittal axis to a slice thickness of 3 mm to reduce the number of
manually-segmented frames (18 vs. 360 slices / image stack) and match the MRI
slice thickness.

While segmentations were performed along the sagittal plane, label map
intersections in the axial and coronal views were used during active creation
of the sagittal segmentation to further improve segmentation accuracy.
Parameters used for 3D model rendering were identical to those used for MR
modeling (Table~\ref{tab:3dslicer}).  The modeled capsule helped guide the CG
segmentation by enabling capsule model intersections in the three orthogonal
planes during CG segmentation (Figure~\ref{fig:arfi_segs}). The capsule
provided an outer boundary for the CG segmentation. The capsule and CG models
dimensions were then measured using the same procedure as the MR images.
\textbf{All B-mode and ARFI image segmentations were reviewed by an experienced
    ARFI imaging researcher (KRN).}
